Malacology: A Programmable Storage System Built on Ceph

### 2016-05-09 paper/paper.tex
sec 3
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

Ceph is a production-quality distributed system and in this section we
touch on some of the subsystems it uses to provide a general-purpose
storage system. In the next section, we describe how we leverage these
subsystems to build new services.

@@

\subsection{Consistency/Versioning of Cluster
State}\label{consistencyversioning-of-cluster-state}

Ceph needs to keep track of cluster state and it does this with separate
``services'': client authentication, logging, MDS maps, MON maps, OSD
maps and placement group (PG) maps. These services are all managed in
the MONs and they all talk to a PAXOS instance; this PAXOS instance goes
and talks to other PAXOS instances on other MONs so that they can all
agree on the correct version of the service; essentially they reach an
agreement about what the state of the cluster is.

@@

\section{Malacology Implementation}\label{malacology-implementation}

\label{implementation}

>>>>

Ceph is a production-quality distributed system and in this section we
touch on some of the subsystems it uses to provide a general-purpose
storage system. In the next section, we describe how we leverage these
subsystems to build new services. This is the an exhuastive list of services.

\subsection{Cluster State Management}
\label{consistencyversioning-of-cluster-state}

A consistent view of cluster state among Ceph daemons and clients is critical
to provide strong consistency guarnatees to clients.  Ceph maintains cluster
state information in per-subsystem ``maps'' (e.g. OSD map, MDS map) that
record membership and status information. A PAXOS-based monitoring service is
responsible integrating state changes into cluster maps, and responding to
requests from out-of-date clients.  As a fundamental building block of many
system designs, consensus abstractions such as PAXOS are a common technique
for maintaining consistent data versions, and are a useful system to expose.
While Ceph does not expose this service directly, it does allow limited use by
clients through a key-value service intended for low-volume, small size
configuration information.

@@

In order to reduce load on the monitoring service, Ceph OSDs use a gossip
protocol to efficiently propogate changes to cluster maps throughout the
system, and automonmously initiate recovery mechansims when failures are
discovered.

@@

\subsection{File System Indexing and Locking}

The distributed metadata service in Ceph provides clients with a POSIX file
system abstraction. Distributed file systems are complex, but fundamentally
provide durable hierarhical indexing and distributed locking service.  The
locking service implements a capabilities that express what data and metadata
clients are allowed to access as well as what they may cache locally.  While
designed for a fixed file abstraction, indexing, locking, and caching are all
common services that are useful to large sets of applications.

\section{Malacology Implementation}
\label{implementation}
